Abstract of Bachelor's Thesis - Academic Year 2018
\begin{center}
\begin{large}
\begin{tabular}{|M{0.97\linewidth}|}
    \hline
        Approximation of high-interaction honeypots\\
        by Command Extension of low-interaction honeypot\\
    \hline
\end{tabular}
\end{large}
\end{center}

~ \\
\renewcommand{\baselinestretch}{0.9}

By the spread of PCs and the system advancement of the IoT device, I was able to make high processing system. The apparatus that the OS's such as the Linux system were equipped with on a device came to be in this way used for people widely. In addition, technique to perform a remote login for the Linux system OS includes SSH. An attack to invade using this illegally is carried out.
A window includes Honeypot what kind of ways an intruder behaves when it was invaded. Honeypot lets an intruder detect it when I succeeded in a login trial by making the environment where it is easy to invade in SSH and collects the log of the command that I carried out on this occasion. In addition, Honeypot which emulated behavior of Shell is used widely now, and there are few commands that this Honeypot can carry out; is implemented. Therefore it is detected by an intruder to Honeypot when invasion is Honeypot. Therefore I expanded the command of Honeypot by the prior experiment and collected invasion log in Honeypot and Honeypot which I expanded of the command which were not expanded. As a result of having compared the log that I collected by using a probabilistic calculation method, I showed that I could acquire a pattern of the command practice log of more intruders. Invasion log of Honeypot which expanded the command tried an approximation of the invasion log when it was invaded of unjust SSH for the real OS in this study how long. I collected invasion log more in Honeypot using the real OS and compared it with Honeypot and expanded Honeypot of the command which were not expanded as an evaluation. I used semantic analysis of the natural language processing in the invasion log of these three, and a semantically thing nearby became clear in invasion log than the invasion log that I collected in Honeypot which the invasion log that I collected in Honeypot which I expanded because a vector expressed a meaning of none of nothing of the command did not expand in Honeypot using the real OS.

\renewcommand{\baselinestretch}{1.0}

~ \\
Keywords : \\
\underline{1． Natural Language Processing},
\underline{2． Semantic analysis},
\underline{3． Honeypot},
\underline{4． SSH}
\begin{flushright}
Keio University, Faculty of Policy Management Studies\\
Yuta Sugafuji
\end{flushright}
